### 2020-05-16 paper.tex
RxJS Example
Clean Up Figures & Examples

\begin{figure}[h]
	\centering
	\emph{TODO}

	\caption{Traditional vs. Reactive Application}
	\label{fig:reactive-application}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\emph{TODO}

	\caption{Reactive Programming Graph}
	\label{fig:reactive-programming}
\end{figure}

@@

\begin{listing}[H]
	\begin{minted}{TypeScript}
		// Add Example
		const x: string = 'Hello World';
	\end{minted}
	\caption{Reactive Programming with RxJS}
	\label{lst:rp-with-rxjs}
\end{listing}

@@

\begin{listing}[H]
	\begin{minted}{TypeScript}
		timer().pipe(
		  map(i => i * 2),
		  map(i => i - 1)
		).subscribe();
	\end{minted}
	\caption{Example RxJS Stream With Breakpoint on Line 2 Within the Arrow Function}
	\label{lst:rxjs-step-controls}
\end{listing}

>>>>

@@

@@

\begin{listing}[H]
	\begin{minted}{TypeScript}
		of('hello', 'foo', 'world').pipe(
			filter(s => s !== 'foo'),
			map(s => s.toUpperCase())
		).subscribe(console.log)             // HELLO, WORLD
	\end{minted}
	\caption{RxJS Code Example}
	\label{lst:rp-with-rxjs}
\end{listing}

@@

\begin{listing}[H]
	\begin{minted}{TypeScript}
		interval(1000).pipe(      // Increasing numbers with 1s delay
		  map(i => i * 2),        // Breakpoint on i * 2
		  map(i => i - 1)
		).subscribe(console.log); // -1, 1, 3, 5, 7, ...
	\end{minted}
	\caption{Example RxJS Stream With Breakpoint on Line 2 Within the Arrow Function}
	\label{lst:rxjs-step-controls}
\end{listing}
